---
title: "gglplot_hook"
author: "Cosmel"
date: '2022-05-19'
output: pdf_document
---

## Setting up the evironment
Notes: setting up my R environment by loading the 'tidyverse' and 'palmerpenguins' packages
#i can load the code by pressing control + alt + i
```{r loading pacakges, warning=FALSE, include=FALSE}
library(tidyverse)
library(ggplot2)
library(palmerpenguins)
```
### Assignin the data that we need
Notes: Using the 'penguins' data

```{r}
data("penguins")
```

### create the data visualization by using ggplot2
Here just using ggplot2 

```{r warning=FALSE}
ggplot(data = penguins) + geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g))
```

### Adding colors to the scatte plot
Improving the scatter plot by adding color the species

```{r warning=FALSE}
ggplot(data = penguins) + geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g,color=species))
```

### Improving by adding shape and color
Adds shape and color to the scatter plot

```{r warning=FALSE}
ggplot(data = penguins) + geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g,color=species,shape=species))
```

### Adding size 

```{r warning=FALSE}
ggplot(data = penguins) + geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g,color=species,shape=species,size=species))
```

### using alpha for transparency

```{r warning=FALSE}
ggplot(data = penguins) + geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g,alpha=species))
```

### assigning a particular color

```{r warning=FALSE}
ggplot(data = penguins) + geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g,alpha=species),color="purple")
```









